### 2023-04-25 chapter2/chapter2.tex
Clarified z-score is a normalization procedure
Added number of regions for OU analysis to methods

We then applied principal components analyses (PCAs) to visualize the major axes of variation of the root and rate parameters for each feature and region. A difficulty with a direct analysis of the parameter estimates, however, is PCAs are sensitive to differences in scaling between variables, and some features have dramatically different intrinsic scales. For example, many compositional features, like fraction\_S, are restricted to the interval [0, 1] whereas SCD is unbounded and can vary from negative to positive infinity. As a result, SCD is responsible for a significant fraction of the overall variance in both parameter distributions (Fig.~\ref{sfig:root_variance}-\ref{sfig:rate_variance}). Therefore, we first transformed the parameters associated with each feature into z-scores relative to the proteome-wide distributions.

@@

The AICs were calculated for the models of each feature using their maximized likelihoods and two and three parameters for the BM and OU models, respectively. The pairwise differences in the AICs yielded a vector with 82 components, each representing the relative goodness of fit of the OU model over the BM model after accounting for their difference in complexity. The vectors were clustered using the correlation distance metric and the UPGMA algorithm. Clusters were manually chosen for subsequent GO analyses. To enrich these clusters for regions with a high likelihood of feature conservation despite low levels of sequence identity, this analysis was restricted to regions whose amino acid and indel substitution rates exceeded 1 and 0.1, respectively (Fig.~\ref{sfig:hierarchy_histogram}).

>>>>

We then applied principal components analyses (PCAs) to visualize the major axes of variation of the root and rate parameters for each feature and region. A difficulty with a direct analysis of the parameter estimates, however, is PCAs are sensitive to differences in scaling between variables, and some features have dramatically different intrinsic scales. For example, many compositional features, like fraction\_S, are restricted to the interval [0, 1] whereas SCD is unbounded and can vary from negative to positive infinity. As a result, SCD is responsible for a significant fraction of the overall variance in both parameter distributions (Fig.~\ref{sfig:root_variance}-\ref{sfig:rate_variance}). Therefore, we first normalized the parameters associated with each feature by transforming them into z-scores relative to their proteome-wide distributions.

@@

The AICs were calculated for the models of each feature using their maximized likelihoods and two and three parameters for the BM and OU models, respectively. The pairwise differences in the AICs yielded a vector with 82 components, each representing the relative goodness of fit of the OU model over the BM model after accounting for their difference in complexity. The vectors were clustered using the correlation distance metric and the UPGMA algorithm. Clusters were manually chosen for subsequent GO analyses. To enrich these clusters for regions with a high likelihood of feature conservation despite low levels of sequence identity, this analysis was restricted to 7,645 regions whose amino acid and indel substitution rates exceeded 1 and 0.1, respectively (Fig.~\ref{sfig:hierarchy_histogram}).
